### 2020-12-20 latex/vlp.tex
Finished the VLP simulations version 1

\section{Simulation Results}
% TODO: Show the simulations of the VLP VNHCs (multiple of them). How does the
% energy injection time of our sin(2theta) VNHC compare to the energy injection
% time of the optimal one? How does the VNHC version compare in robustness with
% the time-based one from the pumping paper?

>>>>

\section{Simulation Results}
In this section, we compare the energy injection properties of our smooth VNHC
\(L_\frac{\pi}{2}(\theta)\), the time-optimal VNHC \(L^\star(\theta)\) from
Equation \eqref{eqn:vlp-optimal-controller}, and the differentiable
VNHC \(L_T(\theta)\) from Equation \eqref{eqn:vlp-T-controller} with 
\(T = 0.01\).
To do this comparison, we simulate an adult Estonian performing a Kiiking
routine.

The average weight of a 25 year old Estonian man is \(80.17\)kg
\cite{estonian-body-data}, so we set the VLP mass \(m\) to this value.
To find our upper and lower bounds on length, we first need to choose the size
of a swing.
The common model of a Kiiking swing is between \(3-4\)m tall
\cite{kiiking-sale}, so we take the length to be \(3\)m.
The average 25 year old Estonian is \(1.8\)m tall \cite{estonian-body-data}, and
we assume their squat height is half that at \(0.9\)m tall.
We further assume that their center of mass (COM) is always located at half
their current height, which means their standing COM is \(0.9\)m from the ground
while their squatting COM is \(0.45\)m from the ground.
This means the distance from their standing COM to the pivot is \(2.1\)m, while
the distance from their squatting COM to the pivot is \(2.55\)m.
Hence, we set \(\underbar{l} = 2.1\) and \(\overbar{l} = 2.55\).
We initialize a VLP with these parameters at 
\((q,p) = \left(\frac{\pi}{32},0\right)\) and plot the resulting orbits
in Figure \ref{fig:vlp-sim-orbit}.

\begin{figure}
   \centering
   \includegraphics[width=0.8\textwidth]{images/kiiking_orbits.png}
   \caption{The orbits of the time-optimal controller \(L^\star(\theta)\)
      (black), the differentiable controller \(L_T(\theta)\) (red),
      and the smooth VNHC \(L_\frac{\pi}{2}(\theta)\) (cyan) employed by a 25
      year old Estonian male on a 3m tall Kiiking swing. All the controllers are
      initialized at \(q(0) = \frac{\pi}{32}\), and they each steadily gain
      energy until they reach a rotation.}
   \label{fig:vlp-sim-orbit}
\end{figure}

The time-optimal controller reaches a rotation within 18 seconds, the
differentiable controller rotates in 41 seconds, and
the smooth VNHC takes 4691 seconds (78 minutes).
Despite the fact that the smooth VNHC is several orders of magnitude slower than
the other controllers, it still succeeds at injecting energy into the
system.
This is especially clear when looking at Figure \ref{fig:vlp-sim-energy}, which
shows the smooth VNHC steadily gaining energy over time.

\begin{figure}
   \centering
   \includegraphics[width=0.8\textwidth]{images/E_kiiking_ltheta.png}
   \caption{The energy \(E_\text{avg}(q,p)\) of a 25 year old Estonian male on a
      3m tall Kiiking swing who employs the smooth VNHC
   \(L_\frac{\pi}{2}(\theta)\).}
   \label{fig:vlp-sim-energy}
\end{figure}

Overall, this simulation confirms that VNHCs are capable of injecting energy
into the VLP. 
Moreover, if one can use the differentiable controller \(L_T(\theta)\) (which
humans certainly can), one is able to approximate the time-optimal controller
arbitrarily well.
We conclude that VNHCs are powerful tools for injecting energy into the VLP
while maintaining the natural structure of human motion.
